gtsummary

### 2020-12-11 rmarkdown-gtsummary.Rmd
updates

>>>>

```{r,echo=FALSE}
tbl_custom <-
  trial %>%
  select(age, grade, trt) %>%
  tbl_summary(by = trt, missing = "no") %>%
  add_overall() %>%
  add_p() %>%
  add_stat_label() %>%
  modify_header(label ~ "**Variable**") %>% 
  modify_spanning_header(c(stat_1, stat_2) ~ "**Treatment Recieved**") %>%
  as_gt() %>%
  gt::tab_header(
    title = gt::md("**Table 1. Patient Characteristics**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")
```

```{r, echo=FALSE, include = FALSE}
tbl_custom %>% 
  gtsave(file = "custom.png")
```
